Approximation as Differentiation notes

### 2025-03-14 notes.tex
We need that Fam(-) preserves products.
Start on set-indexed products.
Introduce Fam(I,C) first.
Just enough notation to state proposition that copairing distributes over parallel composition.
secrefs.

Some of the key constructions:
\begin{itemize}
\item Category of families $\Fam(C)$ for any category $C$
\item Category of $\LatGal$ of bounded lattices and Galois connections
\end{itemize}

% Is one of the goals to define sufficient conditions on $C$ for $\Fam(C)$ to be Cartesian closed?

\noindent $\Set$ will often be $\Setoid$ in the Agda implementation but we will gloss that detail for now.

@@

\input{notes/sec/cmon-enriched}
\input{notes/sec/biproduct}
\input{notes/sec/fam}
\input{notes/sec/galois}

>>>>

Notions covered so far:
\begin{itemize}
\item $\CMon$-enriched categories (\secref{cmon-enriched})
\item biproducts (\secref{biproduct})
\item category $\Fam(I,C)$ of $I$-indexed families of objects of $C$ (\secref{fam})
\item set-indexed products (\secref{set-indexed-product})
\item Grothendieck construction and category of families $\Fam(C)$ (\secref{grothendieck})
\item category of $\LatGal$ of bounded lattices and Galois connections (\secref{galois})
\end{itemize}

\noindent $\Set$ will usually be $\Setoid$ in the Agda implementation but we will gloss that detail for now.

\input{notes/sec/notation}

@@

\input{notes/sec/cmon-enriched}
\input{notes/sec/biproduct}
\input{notes/sec/fam}
\input{notes/sec/set-indexed-product}
\input{notes/sec/grothendieck}
\input{notes/sec/galois}

### 2025-03-14 notes/sec/grothendieck.tex
Put new definition of lambda-inv in LaTeX.
Progress on lambda-inv/natural.
secrefs.

\subsection{Category of families}

@@

\noindent When $F$ is contravariant, a morphism $f: X \to Y$ is a morphism $\idx{f}: \idx{X} \to \idx{Y}$ in
$D$ paired with morphisms $\faml{f}: \faml{X} \to F(f)(\faml{Y})$ in $F(\idx{X})$.

@@

\begin{enumerate}
\item $[X, Y]$ to be the object $(X',Y')$ in $\Fam(C)$ with $X' = \Fam(C)(X,Y)$ and $Y'_f =
\prod_{\idx{X}}\reindex{\faml{Y}}{\idx{f}}$ for every $f: X \to Y$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) sending any $(f, g): X \times Y \to Z$ to
$(f', g'): X \to [Y, Z]$ with:
\begin{itemize}
\item $f'(x) = (f \comp (x, -), \reindex{g}{(x,-)} \comp \inj_{\faml{Y}}):
Y \to Z$ where $\inj_{\faml{Y}}: \faml{Y} \to \const_{\idx{Y}}(\faml{X}_x) \biprod \faml{Y}$
\item $g'_x = \lambda_{\prod_{\idx{Y}}}(\reindex{g}{(x,-)} \comp \inj_{\faml{X}_x}:
\const_{\idx{Y}}(\faml{X}_x) \to \reindex{\faml{Z}}{f})$ where $\inj_{\faml{X}_x}: \const_{\idx{Y}}(\faml{X}_x)
\to \const_{\idx{Y}}(\faml{X}_x) \biprod \faml{Y}$
\end{itemize}
\item The family of morphisms $\eval_{X,Y} = (f',g'): [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $f'((f, g), x) = f(x)$
\item $g'_{(f,g), x} = \coprodM{{\eval_{\prod}}_x}{g_x}:
\prod_{\idx{X}}\reindex{\faml{Y}}{f} \biprod \faml{X}_x \to \faml{Y}_{f(x)}$
\end{itemize}
\end{enumerate}

@@

\begin{enumerate}
\item Define the family of functions $\lambda^{-1}_{X,Y,Z}$ sending any $(f,g): X \to [Y,Z]$ to $(f^\dagger,
g^\dagger): X \times Y \to Z$ with:
\begin{itemize}
\item $f^\dagger(x,y) = f'(y)$
\item $g^\dagger_{x,y} = \coprodM{{\eval_{\prod}}_y \comp g_x}{g'_y}$
% $g'_y \comp \proj_{\faml{Y}_y}$ where $f(x) = (f',g')$ and $\proj_{\faml{Y}_y}: \faml{X}_x \biprod
% \faml{Y}_y \to \faml{Y}_y$
\end{itemize}
\noindent where $f(x) = (f',g')$.

\todo{Show $\lambda^{-1}_{X,Y,Z}(\lambda_{X,Y,Z}(f)) = f$ and $\lambda_{X,Y,Z}(\lambda^{-1}_{X,Y,Z}(f)) =
f$}.

>>>>

\subsection{Category of families}
\label{sec:grothendieck}

@@

\noindent When $F$ is contravariant, a morphism $f: X \to Y$ is a morphism $\idx{f}: \idx{X} \to \idx{Y}$ in
$D$ paired with a morphism $\faml{f}: \faml{X} \to F(f)(\faml{Y})$ in $F(\idx{X})$.

@@

\begin{enumerate}
\item $[X, Y]$ to be the object $(X',Y')$ in $\Fam(C)$ with $X' = \Fam(C)(X,Y)$ and $Y'_{f,g} =
\prod_{\idx{X}}\reindex{\faml{Y}}{f}$ for every $(f,g): X \to Y$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) sending any $(f, g): X \times Y \to Z$ to
$(f', g'): X \to [Y, Z]$ with:
\begin{itemize}
\item $f'(x) = (f \comp (x, -), \reindex{g}{(x,-)} \comp \inj_{\faml{Y}}):
Y \to Z$ where $\inj_{\faml{Y}}: \faml{Y} \to \const_{\idx{Y}}(\faml{X}_x) \biprod \faml{Y}$
\item $g'_x = \lambda_{\prod_{\idx{Y}}}(\reindex{g}{(x,-)} \comp \inj_{\faml{X}_x}:
\const_{\idx{Y}}(\faml{X}_x) \to \reindex{\faml{Z}}{f})$ where $\inj_{\faml{X}_x}: \const_{\idx{Y}}(\faml{X}_x)
\to \const_{\idx{Y}}(\faml{X}_x) \biprod \faml{Y}$
\end{itemize}
\item The family of morphisms $\eval_{X,Y} = (f',g'): [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $f'((f, g), x) = f(x)$
\item $g'_{(f,g), x} = \coprodM{{\eval_{\prod}}_x}{g_x}:
\prod_{\idx{X}}\reindex{\faml{Y}}{f} \biprod \faml{X}_x \to \faml{Y}_{f(x)}$
\end{itemize}
\end{enumerate}

@@

\begin{enumerate}
\item Define the family of functions $\lambda^{-1}_{X,Y,Z}$ sending any $(f,g): X \to [Y,Z]$ to $(f^\dagger,
g^\dagger): X \times Y \to Z$ with:
\begin{itemize}
\item $f^\dagger(x,y) = f'(y)$ where $f(x) = (f',g')$
\item $g^\dagger_{x,y} = \coprodM{{\eval_{\prod}}_y \comp g_x}{g'_y}$ where $f(x) = (f',g')$
\end{itemize}

\todo{
\begin{itemize}
\item $\lambda^{-1}_{X,Y,Z}(\lambda_{X,Y,Z}(f,g)) = (f,g)$ for any $(f,g): X \times Y \to Z$
\item $\lambda_{X,Y,Z}(\lambda^{-1}_{X,Y,Z}(f,g)) = (f,g)$ for any $(f,g): X \to [Y,Z]$
\end{itemize}
}
